An Overview of SemanticPaint

### 2015-12-12 cv3d_seminar/paper.tex
all but SRF and Related
final paper version; shortened and reworked a little

\usepackage{graphicx}   
\usepackage{amsmath}

@@

	\title{SemanticPaint}
	\author{Adam Kosiorek
	\thanks{Advisor: M.Eng.~Keisuke Tateno, Chair for Computer Aided Medical Procedures \& Augmented Reality, TUM, WS 2015/16.}}
	\markboth{Master Seminar: Recent Trends in 3D Computer Vision}{}
	\institute{}
	\maketitle

\begin{abstract}
  We describe SemanticPaint \cite{SemanticPaint} --- a system for capturing and  interactive segmentation of 3D enviornments. It allows adding new object categories at runtime, updates the model with and infers labels of newly seen data in an online fashion. 
\end{abstract}

@@

  The pipeline starts with capturing the environment as a stream of noisy RGBD images and combining them into a  3D model updated in an online fashion. The user can choose which objects to label and can do so by ``touching'' a small part of an object or encircling it with his hand and uttering the label. The label and the affected data points are further passed to a Streaming Random Forest (SRF) classifier which constantly learns and labels all visible voxels. To further improve classification results a spatially dense labeling is produced by an efficient mean-field inference algorithm. One of the biggest strengths of SemanticPaint is the efficiency of each part of the pipeline, which translates to real time performance. Algorithms used in the pipeline were adapted to work on volumetric data in the TSDF format directly in order to avoiding costly conversions to mesh or point-cloud formats. To allow this, the Voxel Oriented Patch features --- a new type of a discriminative feature describing the voxel space --- has been designed.

@@

  \textbf{Acquisition and Reconstruction } Capturing the geometry of the surrounding world has been a long standing problem \cite{old}. An offline processing of multiple images allowed to reconstruct digital heritage and construct world-scale 3D models with remarkable quality \cite{heritage}. The inception of low-cost RGBD sensors and powerful GPUs enabled online 3D scanning, augmented reality and using 3D environment models for navigation purposes \cite{fusion}. \cite{Monofusion} enables 3D reconstruction of small scenes using a single off-the-shelf RGB camera. It uses a sparse tracking method to first estimate the camera's pose and then select key frames and relative to them secondary frames, from which 3D stereo reconstruction is performed. The achieved results are similar to KinectFusion with the only limitation being that the precision of texture-less surfaces' reconstruction is somewhat lacking.

  \noindent
  \textbf{Scene Understanding } Object recognition, detection and segmentation has been done with 2D RGB images, RGBD data, point clouds and volumetric representations. \cite{VCRF} uses a Voxel-based CRF for simultaneous reconstruction and segmentation. Each voxel contains information about visibility and occlusion as well as group membership. The first two are used to to improve reconstruction by mitigating depth-map noise. The visibility values are constrained by that each ray from the camera can hit only one visible vertex. The group membership information encodes priors given by bounding boxes of detected objects. A graph-cut algorithm is used for global inference. The whole scene has to be registered beforehand, since any change in the CRF's structure would require restarting the inference algorithm. No computational performance was reported. \cite{ChangeDetection} is a first step towards online simultaneous registration and segmentation. Using RGBD images, the framework constructs a model of the environment and updates it each time a new frame comes in. When a significant change in the model is detected, the resulting model is split into a static and a dynamic part, where the latter is assumed to have moved in space. The movement is detected by comparing the expected and observed intensity values at each voxel. The system is online, but is far from real time with 0.7 to 2s processing time per frame. \cite{mesh} shows that converting to another data representation can help to improve segmentation accuracy and inference speed. TSDF model is used to reconstruct a 3D scene from a sequence of RGBD images. The volumetric representation is triangulated and a 3D mesh is recovered. Next, visual features are computed directly on images and projected into the 3D model, while geometric features are computed on the mesh directly. Segmentation is done via a CRF. The approach is tested on the augmented KITTI and NYU datasets for indoor and outdoor scene segmentation where it delivers state-of-the-art results.

@@

\section{Space Representation}

  The space is represented by a 3D volume constructed from the sequence of RGBD images using Truncated Signed Distance Function (TSDF) \cite{TSDF}. Large-scale scene handling is facilitated by the hashed volumetric representation of \cite{hashed_voxel} with a 6mm$^{3}$ voxel. Each voxel contains: TSDF distance, colour information in the LAB space, a weight for averaging distance values, a user annotation class, a predicted class, an outcome of the mean-field inference from before and after classification and the probability of each class as inferred by the mean-field algorithm, for each class. The total number of bits per voxel is $96 + \textrm{[number of classes]} \cdot 16$.

@@

  This work relies heavily on classification and since even the most powerful classifier is useless if inappropriate features are supplied this paper contributes Voxel Oriented Patch (VOP) features. They are efficiently computed from the TSDF volume representation (cf. figure \ref{fig:vop}). Let $V_i$ be a VOP and $\mathbf{n}^i$ the normal of voxel i. An image patch of dimensions $r \times r$  is centered on voxel $i$ from the plane $(\mathbf{p} - \mathbf{p}_i) \cdot \mathbf(n)_i = 0$. The patch contains colour values stored in the TSDF on the plane in CIELab to mitigate illumination effects. Additionally, $V_i$ stores distance to the nearest dominant horizontal surface. $r = 13$ with a resolution of $10\frac{mm}{pixel}$ is used. Rotation invariance is achieved exactly as in \cite{sift}. The patch is rotated according to the dominant gradient direction. It is computed by creating a histogram of gradient directions with 36 bins, where the directions are weighted by gradient magnitudes and a gaussian window centered at the voxel. Furthermore, a quadratic polynomial is fit to the three biggest values of the histogram, whose maximum is the final direction.

@@

  Online Random Forest \cite{online_forest} allow runtime model updates and they differ in that for a new node $n$ they generate a distribution of split function $\Theta_n$ and maintain a set of label statistics for each of them, updated when a new sample comes to the node. Label statistics are sufficient to compute information gain and thus the node $n$ is further split if it has seen a predefined number of samples or if the minimal value of the information gain is low enough. Storing and updating statistics in leaf nodes is computationally expensive which limits runtime performance

@@

  Streaming Random Forest begins by creating a reservoir $R_n$ of at most $K$ samples stored in a list $T_n$ at the root node. It represents an unbiased sample of all training data seen so far. Initially, the first $K$ samples are stored. Then, a sample in the reservoir is exchanged with an incoming one with probability $p = \frac{K}{m_n}$, where $m_n$ is the number of samples seen so far at node $n$. Splitting the node requires computing the objective function for each $\theta \in \Theta_n$ over $R_n$. $H(R_n)$ is computed from the normalized class label histogram $P(l|R_n)$. Let $|R_n|$ be the amount of samples stored in the reservoir $n$ and let $R_n^d$ be the splitting induced by $\theta$. Finally, the split function is chosen as $f_n = \arg \max_{\theta \in \Theta_n} G(S, S^L, S^R | \theta)$  and set the number of samples seen by the child node to $|m_n^d| = |R_n^d| \max {\left(1, \frac{m_n}{K}\right)}$. Since the total number of samples stored is bounded by $K$ this approach uses less memory. Constructing child reservoirs from parent reservoirs (cf. fig \ref{fig:forest}) lessens the computational load.

  The GPU implementation can handle up to 17 million voxel classifications per second, while between 3 and 10 million voxels are visible at any one time \cite{hashed_voxel}. To improve performance, voxels are batched and only a single batch is evaluated per frame.

@@

  Neighbourhood of 6 cm is used. Negative log likelihood of eq. \ref{eq:posterior} defines the energy

@@

  Unary and pairwise potentials $\phi_i(x_i)$ and $\phi_{ij}(x_i, x_j)$ encode the cost of assigning a label to $v_i$ and a cost of assuming different labels by voxels in a neighbourhood, respectively. These costs are constantly changing due to the changing predictions of the random forest and user interaction.

  Initially, all voxels are encouraged to take a background label by setting $\phi_i(l) = 0$ for background class and grater than zero otherwise. When the user touches an object, a set of touched voxels $\mathcal{H}_S$ is registered and their unary potentials set to $\phi_i(l) = \infty$ if their labels are different then the specified one, and zero if they are the same, thus imposing the labeling. If user labels a region more than once, the old labels are simply overwritten.

  To process the encircling action, the labeling is projected into the current frame. Next, a GMM is fit with the foreground class taken as a convex hull of the encircled region and background as the rest of the image. For every pixel in a bounding box around the user annotation the unary potentials are updated as

@@

  with $P_E($fg$|\mathbf{a}_i)$ the probability of assuming the foreground label, which stems from the normalized likelihood $P(\mathbf{a}_i|$fg$)$ from the GMM.

  \begin{equation}
    P_E(\text{fg}|\mathbf{a}_i) = \frac{P(\mathbf{a}_i|\text{fg}) }{P(\mathbf{a}_i|\text{fg}) + P(\mathbf{a}_i|\text{bg})}
  \end{equation}

  For all voxels that haven't been explicitly labeled by the user unitary potentials are updated with the predicted values as $\phi_i(l) = -\log P_F(x_i = l | \mathbf{D})$. Finally, smoothness is achieved by the standard Potts model by assigning a discontinuity cost $\phi_{ij}(x_i, x_j) = \lambda_{ij}$ if voxels have different labels and zero otherwise, with $\lambda_{ij}$ a function of difference in position, intensity and normal directions.

@@

  SRF was compared against Online Random Forests (ORF) \cite{online_forest} and Hoeffding trees (HT) \cite{htree}. In order to simulate non-IID data, a dataset of 300 objects of 51 categories \cite{dataset} was used. One revolution of each object was recorded with an RGBD camera from three different viewpoints. Online setting was created by sequentially adding new categories. Two thirds of each viewpoint of each object is used for training. Results are summarized by figure \ref{fig:srf_results}. SRF clearly outperforms its competitors.

\begin{figure}[!ht]
 \center
 \includegraphics[width=0.75\textwidth]{figures/srf_results}
 \caption{Comparison of Streaming Random Forest against Online Random Forest and Hoeffding Trees.}
 \label{fig:srf_results}
\end{figure}

@@

  This paper contributes an interactive system that enables users to create customized models of 3D environments. It can be used to gather groundtruth for large-scale visual recognition systems, robot navigation and to aid partially sighted people. There are some limitations, however. Use of the system is now restricted to simple indoor scenes. Computational load increases with the size of the scene while prediction accuracy drops with the number of object categories.

@@

  The system has also some limitations. Combing colour and depth data requires careful sensor calibration. Combing colour and depth data requires careful sensor calibration. Lack thereof results in misclassification at object boundaries. Additionally, strong changes of lighting conditions impair classification ability at certain viewpoints. These failures are shown in figure \ref{fig:failures}. Moreover, computational performance drops with the increasing size of the scene and classification accuracy decreases with the number of classes. What is more, no global context is used for classification.

@@

  There is big room for improvement. Introducing priors associated with the type of environment or with an object class (\emph{e.g.} vertical walls) could greatly improve classification accuracy. Failure cases from Fig. \ref{fig:failures} could be avoided if pure geometric features were used. Some research is required on scaling the system to bigger scenes and moving to outdoor environments.

@@

  \bibitem{old}
  ROBERTS , L. G. 1963. Machine perception of three-dimensional solids. Ph.D. thesis, Massachusetts Institute of Technology.

  \bibitem{VCRF}
  KIM , B.-S., KOHLI , P., AND SAVARESE , S. 2013. 3D scene understanding by voxel-CRF. In Proc. ICCV.

  \bibitem{Monofusion}
  PRADEEP , V., RHEMANN , C., IZADI , S., ZACH , C., BLEYER , M., AND BATHICHE , S. 2013. Monofusion: Real-time 3D reconstruction of small scenes with a single web camera. In Proc. ISMAR.

  \bibitem{ChangeDetection}
  HERBST , E., HENRY , P., AND FOX , D. 2014. Toward online 3-d object segmentation and mapping. In IEEE International Conference on Robotics and Automation (ICRA).

  \bibitem{mesh}
  VALENTIN , J. P., SENGUPTA , S., WARRELL , J., SHAHROKNI , A., AND TORR , P. H. 2013. Mesh based semantic modelling for indoor and outdoor scenes. In Proc. CVPR.

  \bibitem{heritage}
  LEVOY , M., PULLI , K., CURLESS , B., RUSINKIEWICZ , S., KOLLER , D., EREIRA , L., GINZTON , M., ANDERSON , S., DAVIS , J., G NSBERG , J., ET AL . 2000. The digital Michelangelo project: 3D scanning of large statues. In Proc. SIGGRAPH. ACM.

  \bibitem{fusion}
  NEWCOMBE , R. A., IZADI , S., HILLIGES , O., MOLYNEAUX , D., KIM , D., DAVISON , A. J., KOHLI , P., SHOTTON , J., HODGES , S., AND FITZGIB-BON , A. 2011. KinectFusion: Real-time dense surface mapping and tracking. In Proc. ISMAR.

  \bibitem{TSDF}
  CURLESS , B. AND LEVOY , M. 1996. A volumetric method for building complex models from range images. In Proceedings of the 23rd annual conference on Computer graphics and interactive techniques. ACM, 303–312.

  \bibitem{hashed_voxel}
  NIESSNER , M., ZOLLHOFER , M., IZADI , S., AND STAMMINGER , M. 2013. Real-time 3D reconstruction at scale using voxel hashing. ACM TOG 32, 6

  \bibitem{online_forest}
  SAFFARI , A., LEISTNER , C., SANTNER , J., GODEC , M., AND BISCHOF , H. 2009. On-line random forests. In IEEE ICCV Workshop.

  \bibitem{reservoir}
  VITTER , J. S. 1985. Random sampling with a reservoir. ACM TOMS 11, 1.

  \bibitem{sift}
  LOWE , D. G. 1999. Object recognition from local scale-invariant features. In Proc. ICCV.

  \bibitem{crf}
  LAFFERTY , J., McCALLUM , A., AND PEREIRA , F. C. 2001. Conditional random fields: Probabilistic models for segmenting and labeling sequence data.

  \bibitem{inference}
  KRAHENBÜHL, P. AND KOLTUN , V. 2011. Efficient inference in fully connected CRFs with Gaussian edge potentials. In NIPS.

  \bibitem{kl}
  KOLLER , D. AND FRIEDMAN , N. 2009. Probabilistic Graphical Models: Principles and Techniques. MIT Press

  \bibitem{htree}
  DOMINGOS, P. AND HULTEN , G. 2000. Mining high-speed data streams. In Proc. SIGKDD.

  \bibitem{dataset}
  LAI , K., BO , L., REN , X., , AND FOX , D. 2011. A large-scale hierarchical multi-view rgb-d object dataset. In Proc. ICRA.

  \bibitem{SemanticPaint}
  VALENTIN, J., VINEET, V., CHENG, M.-M., KIM, D., SHOTTON, J., KOHLI, P., NIESSNER, M., CRIMINISI, A., IZADI, S., TORR, P. 2015. SemanticPaint: Interactive 3D Labeling and Learning at your Fingertips. SIGGRAPH.

>>>>

\usepackage{graphicx}   
\usepackage{amsmath}
\usepackage{subcaption}

@@

	\title{An Overview of SemanticPaint}
	\author{Adam Kosiorek
	\thanks{Advisor: M.Eng.~Keisuke Tateno, Chair for Computer Aided Medical Procedures~\&~Augmented Reality, TUM, WS 2015/16.}}
	\markboth{Master Seminar: Recent Trends in 3D Computer Vision}{}
	\institute{}
	\maketitle

\begin{abstract}
  We describe SemanticPaint \cite{SemanticPaint} --- a system for capturing and  interactive segmentation of 3D environments. It allows adding new object categories at runtime, updates the model with and infers labels of newly seen data in an online fashion. 
\end{abstract}

@@

@@

  \textbf{Scene Understanding } Object recognition, detection and segmentation has been done with colour and RGBD images, point clouds, meshes and volumetric representations. \cite{mesh}  uses a TSDF model to reconstruct a 3D scene from a sequence of RGBD images. The volumetric representation is triangulated and a 3D mesh is recovered. Next, visual features are computed on images and projected into the 3D model, while geometric features are computed on the mesh directly. Segmentation is done via a CRF. This approach achieves state-of-the-art results on KITTI and NYU datasets for indoor and outdoor scene segmentation. \cite{VCRF} uses a Voxel-based CRF for offline simultaneous reconstruction and segmentation. Each voxel contains information about visibility and occlusion as well as group membership. The first two are used to improve reconstruction by mitigating depth-map noise. The visibility values are constrained by that each ray from the camera can hit only one visible vertex. The group membership information encodes priors given by bounding boxes of detected objects. \cite{ChangeDetection} is a first step towards online registration and segmentation. Using RGBD images, the framework constructs a model of the environment and updates it with each new frame. When a significant change in the model is detected, it is split into a static and a dynamic part, where the latter is assumed to have moved in space. The movement is detected by comparing the expected and observed intensity values at each voxel. The system is online, but is far from real time with 0.7 to 2s processing time per frame.

  \noindent
  \textbf{Model-based SLAM } KinectFusion \cite{fusion} has brought online 3D reconstruction from a single depth sensor. It uses model-based tracking to match an incoming frame against a global volume in the TSDF \cite{TSDF} format. SLAM++ extends KinectFusion by object classification capabilities. It classifies objects by matching object in the scene against a database of objects in real time. It then builds an object-pose graph, which is a very sparse and compact representation of the world. It works online, but requires a previously prepared object database. \cite{monofusion} enables 3D reconstruction of small scenes using a single RGB camera. It uses a sparse tracking method to first estimate the camera's pose and then select key frames and relative to them secondary frames, from which 3D stereo reconstruction is performed. The achieved results are similar to KinectFusion with the only limitation being the poor precision at texture-less surfaces.

@@

\section{Pipeline Overview}

  \begin{figure}[!ht]
    \center
    \includegraphics[width=0.75\textwidth]{figures/pipeline}
    \caption{The SemanticPaint Pipeline.}
    \label{fig:pipeline}
  \end{figure}

    The pipeline (cf. Fig. \ref{fig:pipeline})  starts with capturing the environment as a stream of noisy RGBD images and combining them into a  3D model updated in an online fashion, similarly to KinectFusion \cite{fusion}. The user can choose which objects to label and does so by ``touching'' a small part of an object or encircling it with his hand and uttering the label. The label and the affected data points are used to update a Conditional Random Field (CRF) segmentation model. They are also passed to a Streaming Random Forest (SRF), an online version of Random Forest classifier, which learns to predict labels of previously unseen elements of the scene. Finally, when the user activates the `test` mode, the SRFs predictions are used to update the CRF. One of the biggest strengths of SemanticPaint is the efficiency of each part of the pipeline, which translates to real time performance. Algorithms used in the pipeline were adapted to work on volumetric data in the TSDF \cite{TSDF} format directly.

@@

  Voxel Oriented Patch (VOP, cf. Fig. \ref{fig:vop}) features are used to guide classification efforts. They are efficiently computed from the TSDF volume representation. Let $V_i$ be a VOP and $\mathbf{n}_i$ the normal of voxel i. An image patch of dimensions $r \times r$  is centered on voxel $i$ and taken from the plane $(\mathbf{p} - \mathbf{p}_i) \cdot \mathbf{n}_i = 0$. The patch contains colour values stored in the TSDF on the plane in CIELab to mitigate illumination effects. Additionally, $V_i$ stores distance to the nearest dominant horizontal surface. $r = 13$ with a resolution of $10\frac{mm}{pixel}$ is used. Rotation invariance is achieved exactly as in \cite{sift}.

@@

@@

  Streaming Random Forest is an inherently online variant of a Random Forest classifier. It begins by creating a reservoir $R_n$ of at most $K$ samples stored in a list $T_n$ at the root node, which represents an unbiased sample of all training data seen so far. Initially, the first $K$ samples are stored. Then, a sample in the reservoir is exchanged with an incoming one with probability $p = \frac{K}{m_n}$, where $m_n$ is the number of samples seen so far at node $n$. Splitting the node requires computing the objective function for each $\theta \in \Theta_n$ over $R_n$. $H(R_n)$ is computed from the normalized class histogram $P(l|R_n)$. Let $|R_n|$ be the amount of samples stored in the reservoir $n$ and let $R_n^d$ be the splitting induced by $\theta$. Finally, the split function is chosen as $f_n = \arg \max_{\theta \in \Theta_n} G(S, S^L, S^R | \theta)$  and set the number of samples seen by the child node to $|m_n^d| = |R_n^d| \max {\left(1, \frac{m_n}{K}\right)}$. Since the total number of samples stored is bounded by $K$ this approach uses only limited memory. Constructing child reservoirs from parent reservoirs (cf. Fig \ref{fig:forest}) lessens computational load.

@@

  By taking negative log likelihood of eq. \ref{eq:posterior} we arrive at the energy

@@

  Unary potential $\phi_i(x_i)$ encodes the cost of assigning a label to $v_i$, while $\phi_{ij}(x_i, x_j)$ is a prior cost of assuming different labels.

  Initially, all voxels are encouraged to take the background label by penalizing all other ones. When the user touches an object, a set of touched voxels $\mathcal{H}_S$ is registered and their unary potentials set to $\phi_i(l) = \infty$ if their labels are different then the specified one, thus imposing the labeling. If user labels a region more than once, the old labels are simply overwritten. To process an encircling action, a GMM is fit with the foreground class taken as a convex hull of the encircled region and the background class as the rest of the image. For every pixel in a bounding box around the user annotation the unary potentials are updated as

@@

  with $P_E($fg$|\mathbf{a}_i)$ the probability of assuming the foreground label.  For all voxels that haven't been explicitly labeled by the user unitary potentials are updated with the predicted values as $\phi_i(l) = -\log P_F(x_i = l | \mathbf{D})$. Finally, smoothness is achieved by the standard Potts model by assigning a discontinuity cost $\phi_{ij}(x_i, x_j) = \lambda_{ij}$ if voxels have different labels and zero otherwise, with $\lambda_{ij}$ a function of difference in position, intensity and normal directions.

@@

  SRF was compared against Online Random Forests (ORF) \cite{online_forest} and Hoeffding trees (HT) \cite{htree}. In order to simulate non-IID data, a dataset of 300 objects of 51 categories \cite{dataset} was used. One revolution of each object was recorded with an RGBD camera from three different viewpoints. Online setting was created by sequentially adding new categories. Two thirds of each viewpoint of each object is used for training. Results are summarized by Fig. \ref{fig:srf_results}. SRF clearly outperforms its competitors.

  \begin{figure}
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=\linewidth]{figures/srf_ap}
      \label{fig:srf_ap}
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=\linewidth]{figures/srf_iu}
      \label{fig:srf_iu}
    \end{subfigure}
    \caption{Comparison of Streaming Random Forest against Online Random Forest and Hoeffding Trees}
    \label{fig:srf_results}
  \end{figure}

@@

  This paper contributes an interactive system that enables users to create customized models of 3D environments. It can be used to gather groundtruth for large-scale visual recognition systems, robot navigation and to aid partially sighted people.

@@

  The system has some limitations, however. Combing colour and depth data requires careful sensor calibration. Combing colour and depth data requires careful sensor calibration. Lack thereof results in misclassification at object boundaries. Additionally, strong changes of lighting conditions impair classification ability at certain viewpoints. These failures are shown in Fig. \ref{fig:failures}. Moreover, computational performance drops with the increasing size of the scene and classification accuracy decreases with the number of classes. What is more, no global context is used for classification.

@@

  There is some room for improvement. Introducing priors associated with the type of environment or with an object class (\emph{e.g.} vertical walls) could greatly improve classification accuracy. Failure cases from Fig. \ref{fig:failures} could be avoided if pure geometric features were used. Some research is required on scaling the system to bigger scenes and moving to outdoor environments.

@@

  \bibitem{VCRF}
  Kim, B.-S., Kohli, P., and Savarese, S. 2013. 3d Scene Understanding By Voxel-Crf. In Proc. ICCV.

  \bibitem{monofusion}
  Pradeep, V., Rhemann, C., Izadi, S., Zach, C., Bleyer, M., and Bathiche, S. 2013. Monofusion: Real-Time 3d Reconstruction Of Small Scenes With A Single Web Camera. In Proc. ISMAR.

  \bibitem{ChangeDetection}
  Herbst, E., Henry, P., and Fox, D. 2014. Toward Online 3-D Object Segmentation and Mapping. In IEEE International Conference On Robotics and Automation (ICRA).

  \bibitem{mesh}
  Valentin, J. P., Sengupta, S., Warrell, J., Shahrokni, A., and Torr, P. H. 2013. Mesh Based Semantic Modelling For Indoor and Outdoor Scenes. In Proc. CVPR.

  \bibitem{fusion}
  Newcombe, R. A., Izadi, S., Hilliges, O., Molyneaux, D., Kim, D., Davison, A. J., Kohli, P., Shotton, J., Hodges, S., and Fitzgib-Bon, A. 2011. Kinectfusion: Real-Time Dense Surface Mapping and Tracking. In Proc. ISMAR.

  \bibitem{TSDF}
  Curless, B. and Levoy, M. 1996. A Volumetric Method For Building Complex Models From Range Images. In Proceedings Of The 23rd Annual Conference On Computer Graphics and Interactive Techniques. ACM, 303–312.

  \bibitem{online_forest}
  Saffari, A., Leistner, C., Santner, J., Godec, M., and Bischof, H. 2009. On-Line Random Forests. In IEEE ICCV Workshop.

  \bibitem{reservoir}
  Vitter, J. S. 1985. Random Sampling With A Reservoir. ACM Toms 11, 1.

  \bibitem{sift}
  Lowe, D. G. 1999. Object Recognition From Local Scale-Invariant Features. In Proc. ICCV.

  \bibitem{crf}
  Lafferty, J., Mccallum, A., and Pereira, F. C. 2001. Conditional Random Fields: Probabilistic Models For Segmenting and Labeling Sequence Data.

  \bibitem{inference}
  Krahenbühl, P. and Koltun, V. 2011. Efficient Inference In Fully Connected Crfs With Gaussian Edge Potentials. In NIPS.

  \bibitem{htree}
  Domingos, P. and Hulten, G. 2000. Mining High-Speed Data Streams. In Proc. SIGKDD.

  \bibitem{dataset}
  Lai, K., Bo, L., Ren, X.,, and Fox, D. 2011. A Large-Scale Hierarchical Multi-View Rgb-D Object Dataset. In Proc. ICRA.

  \bibitem{SemanticPaint}
  Valentin, J., Vineet, V., Cheng, M.-M., Kim, D., Shotton, J., Kohli, P., Niessner, M., Criminisi, A., Izadi, S., Torr, P. 2015. SemanticPaint: Interactive 3d Labeling and Learning At Your Fingertips. SIGGRAPH.
